What's she talking about? Category based discourse inferences in early childhood

### 2020-02-21 paper/manuscript.Rmd
clean Rmd

#bf_ex1 <- bayes_factor(ex1_m1, ex1_m2, log = FALSE, maxiter = 5000)

@@

# post_plot <- ggplot(plot_dens, aes(posterior, group = age)) +
#   geom_vline(xintercept = 1/3, lty=2, size = 1)+
#   geom_area(data = densities_df %>% filter(ci_shade == "ON"), aes(x = x, y = y, fill = age), alpha = .5) + 
#   geom_density(alpha = .5, size = 1)+
#   labs(y="Probability density", x="Proportion correct")+
#   theme_few() +
#   xlim(-0.05,1.05)+
#   guides(alpha = F)+
#   scale_fill_colorblind(name = "Age")

@@

p3 <- ggplot() +
  geom_hline(yintercept = 1/3, lty=2, size = 1)+
  geom_jitter(data = pex2_1,aes(x = age_num, y= correct, col = condition), width = .00, height = .01, alpha = .5)+
  geom_line(data = sample2, aes(x = age, y = y, col = condition, group = sample), size = .025)+
  geom_line(data = map_model_2, aes(x = age, y = y, col = condition), size = 1)+
  #geom_smooth(data = ex2_data,aes(x = age_num, y= correct, col = condition), method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, size = 1.5)+
  geom_pointrange(data = pex2_2, aes(x = age_group+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .2), pch = 4)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)+
  scale_color_ptol(name = "Speaker",
                   breaks = c("different_speaker", "same_speaker"),
                   labels = c("Different", "Same"))
```

>>>>

@@

@@

p3 <- ggplot() +
  geom_hline(yintercept = 1/3, lty=2, size = 1)+
  geom_jitter(data = pex2_1,aes(x = age_num, y= correct, col = condition), width = .00, height = .01, alpha = .5)+
  geom_line(data = sample2, aes(x = age, y = y, col = condition, group = sample), size = .025)+
  geom_line(data = map_model_2, aes(x = age, y = y, col = condition), size = 1)+
  geom_pointrange(data = pex2_2, aes(x = age_group+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = condition),size = .8, position = position_dodge(width = .2), pch = 4)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)+
  scale_color_ptol(name = "Speaker",
                   breaks = c("different_speaker", "same_speaker"),
                   labels = c("Different", "Same"))
```
